Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-05-24 paper/AlignedIsotropicGW.tex
Close #23, figure captions formatting.

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} Approximate posteriors on
    $\chieff$ from the Advanced LIGO O1 run observations\cite{O1-BBH}.
    We approximate the posteriors reported using Gaussians with the
    same median and 90\% credible interval.  It is notable that none
    of the $\chieff$ posteriors support high \ac{BH} spin magnitudes
    with aligned spins, suggested by observations of stellar-mass
    black holes in X-ray binaries\cite{2015PhR...548....1M}.}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/chi-eff-distributions}
  \caption{\label{fig:chieff-distribution-models} The models for the
    population distribution of $\chieff$ considered in this paper.  In
    all models we assume that the binary mass ratio
    $q \equiv m_1/m_2 = 1$ and that the distribution of spin vectors
    is the same for each component.  The ``flat'' (blue lines),
    ``high,'' (green lines), and ``low'' (red lines) magnitude
    distributions are defined in Eq.\ \eqref{eq:magnitude-dists}.
    Solid lines give the $\chieff$ distribution under the assumption
    that the orientations of the spins are isotropic; dashed lines
    give the distribution under the assumption that both objects'
    spins are aligned with the orbital angular momentum.  The
    isotropic distributions are readily distinguished from the aligned
    distributions by the production of negative $\chieff$ values,
    while the distinction between the three models for the spin
    magnitude distribution is less sharp.}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/Wills_evidence_ratio_figure_with_mixture_models}
  \caption{Odds ratios among our models using the approximations to
    the posteriors on $\chieff$ from the O1 observations shown in
    Figure \ref{fig:O1-posteriors}.  The flat (``F''), high (``H''),
    and low (``L'') spin magnitude distributions (see Eq.\
    \eqref{eq:magnitude-dists}) are paired with isotropic (``I'') and
    aligned (``A'') angular distributions, as well as a mixture model
    of the two (``$\mathrm{M}$'').  The most-favoured models have the
    ``low'' distribution of spin magnitudes.  The odds ratio between
    these models is $\OOneOddsIsoAligned$, or
    $\OOneSigmaIsoAligned\sigma$.  For all magnitude distributions the
    pure-isotropic models are preferred over the mixture models;
    correspondingly, the posterior on the mixture fraction peaks at
    100\% isotropic.}
  \label{fig:O1-odds}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/six-way-O2-model-selection}
  \caption{\label{fig:O2-predictions} Distribution of odds ratios
    predicted with 10 additional observations above the three
    discussed above.  Each panel corresponds to additional
    observations drawn from one of the $\chieff$ distribution models.
    The model from which the additional observations are drawn is
    outlined in red.  The height of the blue bar gives the median odds
    ratio relative to the model from which the additional observations
    are drawn; the green line gives the 68\% ($1 \sigma$) symmetric
    interval of odds ratios over 1000 separate draws from the model
    distribution.  The closest median ratio between the most-favoured
    isotropic model and the most-favoured aligned model is
    $\OTwoOddsIsoAlignedMin$, corresponding to
    $\OTwoSigmaIsoAlignedMin\sigma$ preference for the correct angular
    distribution; most models result in more than $5\sigma$ preference
    for the correct angular distribution.  Because the three existing
    observations are included in each data set the ``correct'' model
    is not necessarily preferred over the others, particularly when
    that model uses the ``high'' magnitude distribution, which is
    strongly dis-favoured from the O1 observations alone.}
\end{figure}

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/posterior_on_isotropic_fraction.png}
\caption{Fraction of the BBH population coming from an isotropic
  distribution under a mixture model. The dotted line shows the flat
  prior on the fraction of BBHs coming from an isotropic distribution,
  $f_i$, under the mixture model. The 3 red lines show the posterior
  on $f_i$ after O1 with our various assumptions regarding BH spin
  magnitudes.  The solid line shows the posterior assuming that all
  BHs have their spin magnitude drawn from the ``flat''
  distribution. The dashed line assumes the ``high'' BH spin magnitude
  distribution $p(a) = 2a$. The dot-dash line assumes the ``low''
  distribution $p(a) = 2(1-a)$.  We see that for a wide range of
  assumptions regarding BH spin magnitudes, the fraction coming from
  an isotropic distribution $f_i$ peaks at 1.}
\label{fig:mixture_fraction_posterior}
\end{figure}
%

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{Effect of small spins on evidence ratio of aligned against
  isotropic models. The blue line shows the evidence ratio (plotted as
  the equivalent sigma) between a model where all systems are aligned,
  versus one where all systems are from an isotropic distribution as a
  function of the power law $\alpha$ corresponding to
  Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin
  magnitude $\bar{a}$ which this $\alpha$ corresponds to. We see that
  for mean spin magnitudes $\lesssim 0.2$ we find no evidence for
  either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

@@

\begin{figure}
  \plotone{../plots/chi-eff-distributions-q05}
  \caption{Distributions of $\chieff$ assuming all merging black holes
    have equal masses ($q=1$) or a 2:1 mass ratio ($q = 0.5$).  The
    details of the distribution are sensitive to the mass ratio, but
    in our analysis we are primarily sensitive to the changing
    \emph{sign} of $\chieff$ under the isotropic models.  This latter
    property is unchanged under changing mass ratio.}
  \label{fig:mass-ratio-sensitivity}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/chi-eff-90cl}
  \caption{Widths of the 90\% credible intervals for $\chieff$ for 500
    binaries in a simulated detected population. $\chieff$ is better
    constrained for systems with low $\chieff$ and low mass ratio.}
  \label{fig:chi-eff-constraints}
\end{figure}

>>>>

\begin{figure}
  \plotone{../plots/chi-eff-mock-posteriors}
  \caption{\label{fig:O1-posteriors} \textbf{Approximate posteriors on
      $\chieff$ from the Advanced LIGO O1 run
      observations\cite{O1-BBH}.}  We approximate the posteriors
    reported using Gaussians with the same median and 90\% credible
    interval.  It is notable that none of the $\chieff$ posteriors
    support high \ac{BH} spin magnitudes with aligned spins, suggested
    by observations of stellar-mass black holes in X-ray
    binaries\cite{2015PhR...548....1M}.}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/chi-eff-distributions}
  \caption{\label{fig:chieff-distribution-models} \textbf{The models for the
    population distribution of $\chieff$ considered in this paper.}  In
    all models we assume that the binary mass ratio
    $q \equiv m_1/m_2 = 1$ and that the distribution of spin vectors
    is the same for each component.  The ``flat'' (blue lines),
    ``high,'' (green lines), and ``low'' (red lines) magnitude
    distributions are defined in Eq.\ \eqref{eq:magnitude-dists}.
    Solid lines give the $\chieff$ distribution under the assumption
    that the orientations of the spins are isotropic; dashed lines
    give the distribution under the assumption that both objects'
    spins are aligned with the orbital angular momentum.  The
    isotropic distributions are readily distinguished from the aligned
    distributions by the production of negative $\chieff$ values,
    while the distinction between the three models for the spin
    magnitude distribution is less sharp.}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/Wills_evidence_ratio_figure_with_mixture_models}
  \caption{\textbf{Odds ratios among our models using the
      approximations to the posteriors on $\chieff$ from the O1
      observations shown in Figure \ref{fig:O1-posteriors}.}  The flat
    (``F''), high (``H''), and low (``L'') spin magnitude
    distributions (see Eq.\ \eqref{eq:magnitude-dists}) are paired
    with isotropic (``I'') and aligned (``A'') angular distributions,
    as well as a mixture model of the two (``$\mathrm{M}$'').  The
    most-favoured models have the ``low'' distribution of spin
    magnitudes.  The odds ratio between these models is
    $\OOneOddsIsoAligned$, or $\OOneSigmaIsoAligned\sigma$.  For all
    magnitude distributions the pure-isotropic models are preferred
    over the mixture models; correspondingly, the posterior on the
    mixture fraction peaks at 100\% isotropic.}
  \label{fig:O1-odds}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/six-way-O2-model-selection}
  \caption{\label{fig:O2-predictions} \textbf{Distribution of odds
      ratios predicted with 10 additional observations above the three
      discussed above.}  Each panel corresponds to additional
    observations drawn from one of the $\chieff$ distribution models.
    The model from which the additional observations are drawn is
    outlined in red.  The height of the blue bar gives the median odds
    ratio relative to the model from which the additional observations
    are drawn; the green line gives the 68\% ($1 \sigma$) symmetric
    interval of odds ratios over 1000 separate draws from the model
    distribution.  The closest median ratio between the most-favoured
    isotropic model and the most-favoured aligned model is
    $\OTwoOddsIsoAlignedMin$, corresponding to
    $\OTwoSigmaIsoAlignedMin\sigma$ preference for the correct angular
    distribution; most models result in more than $5\sigma$ preference
    for the correct angular distribution.  Because the three existing
    observations are included in each data set the ``correct'' model
    is not necessarily preferred over the others, particularly when
    that model uses the ``high'' magnitude distribution, which is
    strongly dis-favoured from the O1 observations alone.}
\end{figure}

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/posterior_on_isotropic_fraction.png}
\caption{\textbf{Fraction of the BBH population coming from an isotropic
  distribution under a mixture model.} The dotted line shows the flat
  prior on the fraction of BBHs coming from an isotropic distribution,
  $f_i$, under the mixture model. The 3 red lines show the posterior
  on $f_i$ after O1 with our various assumptions regarding BH spin
  magnitudes.  The solid line shows the posterior assuming that all
  BHs have their spin magnitude drawn from the ``flat''
  distribution. The dashed line assumes the ``high'' BH spin magnitude
  distribution $p(a) = 2a$. The dot-dash line assumes the ``low''
  distribution $p(a) = 2(1-a)$.  We see that for a wide range of
  assumptions regarding BH spin magnitudes, the fraction coming from
  an isotropic distribution $f_i$ peaks at 1.}
\label{fig:mixture_fraction_posterior}
\end{figure}
%

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned
    against isotropic models.} The blue line shows the evidence ratio
  (plotted as the equivalent sigma) between a model where all systems
  are aligned, versus one where all systems are from an isotropic
  distribution as a function of the power law $\alpha$ corresponding
  to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin
  magnitude $\bar{a}$ which this $\alpha$ corresponds to. We see that
  for mean spin magnitudes $\lesssim 0.2$ we find no evidence for
  either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

@@

\begin{figure}
  \plotone{../plots/chi-eff-distributions-q05}
  \caption{\textbf{Distributions of $\chieff$ assuming all merging
      black holes have equal masses ($q=1$) or a 2:1 mass ratio
      ($q = 0.5$).}  The details of the distribution are sensitive to
    the mass ratio, but in our analysis we are primarily sensitive to
    the changing \emph{sign} of $\chieff$ under the isotropic models.
    This latter property is unchanged under changing mass ratio.}
  \label{fig:mass-ratio-sensitivity}
\end{figure}

@@

\begin{figure}
  \plotone{../plots/chi-eff-90cl}
  \caption{\textbf{Widths of the 90\% credible intervals for $\chieff$
      for 500 binaries in a simulated detected population.} $\chieff$
    is better constrained for systems with low $\chieff$ and low mass
    ratio.}
  \label{fig:chi-eff-constraints}
\end{figure}
